Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-07-06 paper/paper.tex
Corrects positionining in m_ee.json with e_wt.json

% Define title, empty date and authors
\title {
  Competition can provide a stopping mechanism for the retinotectal
  projection \\
  or \\
  Competition provides a stopping mechanism for the chemoaffinity
  theory which is robust to noise \\
  or \\
  Self-organisation of topographically ordered axon connections can take place
  in a noisy environment if axons compete
}
\date{} % No date please
\author{\Authors}

@@

@@

This is where I really want to say ``the only interactions in the model are
via forward (ligand-activates-receptor) and reverse
(receptor-activates-ligand) signalling''. Somehthing like:

@@

% Discuss the Hill Equation! https://en.wikipedia.org/wiki/Hill_equation_(biochemistry)

>>>>

% Define title, empty date and authors
\title {
  Competition can account for stopping in a gradient-following model
  of the retinotectal projection \\
  \emph{or} \\
  Competition provides stopping for the chemoaffinity
  theory which is robust to noise \\
  \emph{or} \\
  Self-organisation of topographically ordered axon connections can take place
  in a noisy environment if axons compete \\
  Time to stop; modelling chemoaffinity with competition \\
}
\date{} % No date please
\author{\Authors}

% Simplified chemoaffinity explains retinotectal mapping via local axon-axon
% interactions
%
% Focus on the chemoaffinity idea for this model. Show that local interactions
% can provide an account for growth cones finding their targets.

@@

Model which carefully deals with receptor
binding: \cite{naoki_revisiting_2017}.

Gradient based models: \cite{nakomoto_topographically_1996}

@@

This is where I really want to say ``the only interactions in the model are
via forward (ligand-activates-receptor) and reverse
(receptor-activates-ligand) signalling''. Something like:

@@

% Discuss the Hill Equation! https://en.wikipedia.org/wiki/Hill_equation_(biochemistry)
% This relates to the work \cite{naoki_revisiting_2017}
